---
title: "Yelp Analysis"
author: "He Guo"
date: "12/16/2019"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(tidytext)
library(knitr)
library(scales)
library(janeaustenr)
library(dplyr)
library(stringr)
library(ggplot2)
library(tidyr)
library(wordcloud)
library(reshape2)
library(yelpr)
library(leaflet)
library(ggmosaic)
library(dplyr)
library(ggthemes)
library(ggmap)
library(tidyverse)  # data manipulation
library(cluster)    # clustering algorithms
library(factoextra)
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(httr,jsonlite,dplyr)
devtools::install_github('OmaymaS/yelpr')
```

## Yelp API

The current study get business data from Yelp API.  The study use longitude and latitude data from Yelp API to plot the map of business in Boston.

## API Data for Boston

The current study get business data from Yelp API.  The study use longitude and latitude data from Yelp API to plot the map of business in Boston.

## Business in Boston

```{r echo=FALSE, results='hide',message=FALSE}
client.id <- 'CYnB6kSW2xzzFpNRSHjrEQ'
client.key <- 'tGos9a9uRI6VWuBkK1EcYdNXIa1pWFOUMRoziue6b6hVoaT1aWp0EXLrO-buK_RYxK_3mgepSdxx5T5xlMstACpRR-eIRDXd4-zfr7a7EEqO3xb5JZxJswSvQ73eXXYx'
location.ma<-"Boston, MA"
limit <- 50
yelp.ma<-business_search(client.key,location.ma,limit)
business.ma<-yelp.ma$businesses
coordinates.ma<-business.ma$coordinates
qmplot(longitude, latitude, data =coordinates.ma)
```


## API Data for New York

The current study get business data from Yelp API.  The study use longitude and latitude data from Yelp API to plot the map of business in New York.


## Business in NYC

```{r echo=FALSE, results='hide',message=FALSE}

location.nyc<-"New York, NY"
limit <- 50
yelp.nyc<-business_search(client.key,location.nyc,limit)
business.nyc<-yelp.nyc$businesses
coordinates.nyc<-business.nyc$coordinates
qmplot(longitude, latitude, data =coordinates.nyc)
```


## Cluster Analysis for business dataset

This study want to apply cluster analysis to get the sub group of yelp business data set.  The study want to see each business in yelp business dataset in  the same subgroup to be similar, and  businesses in yelp business dataset from different subgroup to be different.


## Cluster for Business in Yelp

```{r, echo = FALSE}
yelp.business<-read.csv("business.csv")
cluster.B<-yelp.business %>%
  select(business_id,stars, review_count)
rownames(cluster.B) <- c()
rownames(cluster.B) <- cluster.B[,1]
cluster.B <- cluster.B[,-1]
cluster.B<-na.omit(cluster.B)
k2 <- kmeans(cluster.B, centers = 4, nstart = 25)
fviz_cluster(k2, data = cluster.B)
```



## Distribution of Stars of business in Yelp vs Has photo or not 

```{r, echo = FALSE}
yelp.photo<-read.csv("photo.csv")
yelp.photo$business_id<-as.character(yelp.photo$business_id)
yelp.business$business_id<-as.character(yelp.business$business_id)
business.photo<-left_join(yelp.business,yelp.photo, by = "business_id")
business.photo$has.photo[is.na(business.photo$photo_id)==TRUE]<-"Doesn't have Photo"
business.photo$has.photo[is.na(business.photo$photo_id)==FALSE]<-"Has Photo"
business.photo$stars<-as.factor(business.photo$stars)
business.photo$has.photo<-as.factor(business.photo$has.photo)
 ggplot(data = business.photo) +
   geom_mosaic(aes(x = product(stars), fill=has.photo))   + 
    scale_fill_manual(values=c( "#9999CC", "#66CC99"))+theme(text=element_text(size=16))+theme(axis.text.x = element_text(angle = 45, hjust = 1))+
   labs(x = "Stars for Each Business")+  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
```


## Distribution of Stars of business in Yelp vs Label of Photo

```{r, echo = FALSE}


business.photo$label<-as.factor(business.photo$label)
business.photo$stars<-as.factor(business.photo$stars)
business.photo$has.photo<-as.factor(business.photo$has.photo)
Yelp.Lable<-business.photo%>%select(stars,label)
Yelp.Lable<-na.omit(Yelp.Lable)
ggplot(data = Yelp.Lable) +
   geom_mosaic(aes(x = product(stars), fill=label)) +
   labs(x = "Stars for Each Business") +theme(text=element_text(size=16))+theme(axis.text.x = element_text(angle = 45, hjust = 1))+  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())+ 
    scale_fill_viridis_d(option="plasma")+
  scale_color_viridis_d(option="plasma")
```



## Yelp Review Analysis

This study use review file in Yelp dataset and applies text analysis to analysis the review from users in Yelp.

## Sentiment

According to the following plot, users post positive review to business in High and mid Rate.  Users post a higher positive sentiment score to business in High Rate.  There are some negative score to business in low Rate.  It means that people will post neigative review to  business in low Rate.  

## Sentiment Plot

```{r, echo = FALSE}
review <- read.csv("review.csv")
review$Rate[review$stars>4]<-"High"
review$Rate[review$stars>=3 & review$stars<=4 ]<-"Mid"
review$Rate[review$stars<3]<-"Low"
re.mining<-data.frame(review$Rate,review$text)
re.mining$review.text<-as.character(re.mining$review.text)
T.mining <-re.mining %>%group_by(review.Rate)%>%mutate(linenumber = row_number())%>%unnest_tokens(word, review.text) 
T.mining_sentiment <- T.mining %>%
  inner_join(get_sentiments("bing"), by = "word") %>%
  count(review.Rate, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
ggplot(T.mining_sentiment, aes(index, sentiment, fill = review.Rate)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~review.Rate, ncol = 2, scales = "free_x")
```

## Words Contirbutes
How much each word contributed to positive and negative sentiment?

## Words Contirbutes Plot 

```{r, echo = FALSE}
bing_word_counts <- T.mining %>%
  inner_join(get_sentiments("bing"),by = "word") %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()
bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()
```

## Words Clouds


```{r, echo = FALSE}

suppressWarnings(
T.mining %>%
  anti_join(stop_words,by = "word") %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100)))
```



## Consecutive Words

The most common consecutive words for business in different rate group


## Consecutive Words Plot
```{r, echo = FALSE}


mining_bigrams <- re.mining %>%
  unnest_tokens(bigram,review.text , token = "ngrams", n = 2)

bigrams_separated <- mining_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)


bigram_counts <- bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)
bigrams_united <- bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ")
mining_tf_idf <- bigrams_united %>%
  count(review.Rate, bigram) %>%
  bind_tf_idf(bigram, review.Rate, n) %>%
  arrange(desc(tf_idf))

mining_tf_idf %>%
  group_by(review.Rate) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(bigram = reorder(bigram, tf_idf)) %>%
  ggplot(aes(bigram, tf_idf, fill = review.Rate)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~review.Rate, scales = "free_y") +
  labs(y = "tf_idf",
       x = NULL) +
  coord_flip()
```

